Computing Entropies With Nested Sampling

### 2017-07-11 paper/ms.tex
Minor edit
Tiny bit of writing in the second appendix

Throughout this paper, the question of how to sample from the constrained
distributions required by NS has not been discussed in detail. For the examples,
I used the original \citet{skilling2006nested} suggestion of using a short MCMC run
initialised at a surviving point. In some problems, this will not be effective,
and this will cause the resulting estimates to be incorrect, as in standard
Nested Sampling applications. Despite this, the algorithm should still be
useful in a wide range of applications.

@@

>>>>

Throughout this paper, the question of how to sample from the constrained
distributions required by NS has not been discussed in detail. For the examples,
I used the original \citet{skilling2006nested} suggestion of using a short MCMC run
initialised at a surviving point. In some problems, this will not be effective,
and this will cause the resulting estimates to be incorrect, as in standard
Nested Sampling applications. Despite this, the algorithm should be
useful in a wide range of applications.

@@

The numerical parameters, and the choice of which problem is being solved,
are specified in {\tt main.cpp}. The default problem is the first example
from the paper.
